Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2022-04-01 vertical-thermal-review.Rmd
replace reference
@NidhiVinod , here I replace a commentary on a paper with the paper itself.

$T_{leaf}$ is strongly tied, and usually within a few degrees of, $T_{air}$ [@cavaleriColdbloodedForestsWarming2020], but can be substantially warmer or cooler under certain conditions (Fig. `r fig_leaf_T`; Note `r Notes_leafTbiophysics`). 
Deviation of $T_{leaf}$ from $T_{air}$ is influenced by other micrometeorological drivers and by leaf traits and stomatal conductance (Note `r Notes_leafTbiophysics`), all of which vary across forest vertical gradients (Fig. `r fig_schematic`).
Leaves adjust to their environment to approach, when possible, an optimal $T_{leaf}$ for photosynthesis and metabolism [@michaletzPlantThermoregulationEnergetics2015a <!--@perezPhotosyntheticHeatTolerances2020; @drakeNoEvidenceHomeostatic2020-->].

>>>>

$T_{leaf}$ is strongly tied, and usually within a few degrees of, $T_{air}$ [@drakeNoEvidenceHomeostatic2020], but can be substantially warmer or cooler under certain conditions (Fig. `r fig_leaf_T`; Note `r Notes_leafTbiophysics`). 
Deviation of $T_{leaf}$ from $T_{air}$ is influenced by other micrometeorological drivers and by leaf traits and stomatal conductance (Note `r Notes_leafTbiophysics`), all of which vary across forest vertical gradients (Fig. `r fig_schematic`).
Leaves adjust to their environment to approach, when possible, an optimal $T_{leaf}$ for photosynthesis and metabolism [@michaletzPlantThermoregulationEnergetics2015a <!--@perezPhotosyntheticHeatTolerances2020; @drakeNoEvidenceHomeostatic2020-->].
